---
title: "Q3"
output: pdf_document
---


```{r,tidy=TRUE}
train_data<-read.table("D:/AY20_MBDS_questions/Question 3/train_data.txt")
train_truth<-read.table("D:/AY20_MBDS_questions/Question 3/train_truth.txt")
test_data<-read.table("D:/googledownload/AY20_MBDS_questions/Question 3/test_data.txt")
x1<-train_data$V1
x2<-train_data$V2
x3<-train_data$V3
x11<-x1*x1
x22<-x2*x2
x33<-x3*x3
x12<-x1*x2
x23<-x2*x3
x13<-x1*x3
y<-train_truth$V1
fit = lm(y ~ x1+x2+x3+x12+x23+x13+x11+x22+x33)
summary(fit)
step(fit, direction="both",k=2)
fit1<-lm(y ~ x1 + x2 + x3 + x12 + x13 + x11)
summary(fit1)
```
In this Question, I use linear regression model to fit the dataset. I use full model $y_i=\beta_0+\beta_1x_{1i}+\beta_2x_{2i}+\beta_3x_{3i}+\beta_{12}x_{1i}*x_{2i}+\beta_{13}x_{1i}*x_{3i}+\beta_{23}x_{2i}*x_{3i}+\beta_{11}x_{1i}^2+\beta_{22}x_{2i}^2+\beta_{33}x_{3i}^2+\epsilon$ and then I do model selection in both directions by AIC criteria. I found the AIC of the model $y_i=\beta_0+\beta_1x_{1i}+\beta_2x_{2i}+\beta_3x_{3i}+\beta_{12}x_{1i}*x_{2i}+\beta_{13}x_{1i}*x_{3i}+\beta_{11}x_{1i}^2+\epsilon$ is the lowest. It means that the complexity of this model is lower than the full model. Then, summarizing this model, I can see that there is strong evidence that the coefficients of $x_1$,$x_2$,$x_1*x_3$ are statistically significant since the P-values of them are extremely small. There is also weak evidence that the the coefficients of $x_1^2$ and $x_1*x_2$ are statistically significant since P-values of them are a bit more than 0.05. Although P-values of coefficient of $x_3$ is a bit more than 0.1, I still decide not to remove it from the model. 

Finally, I use this model to output the result of the input test data.

I show the output of the first three of test datasets below.

```{r,tidy=TRUE}


predict(fit1,newdata=data.frame(x1=test_data[1:3,1],x2=test_data[1:3,2],x3=test_data[1:3,3],x12=test_data[1:3,1]*test_data[1:3,2],x13=test_data[1:3,1]*test_data[1:3,3],x11=test_data[1:3,1]*test_data[1:3,1]))
```